Component response rate variation drives stability in large complex systems

### 2018-05-18 ms.Rmd
Fix Fig 3 legend

**Figure 3: Stability of large complex systems with and without variation in component response rate ($\boldsymbol{\gamma}$).** The $\ln$ number of systems that are stable across different system sizes ($S$) given $C = 1$, and the proportion of systems in which variation in $\gamma$ is critical for system stability. For each $S$, 1 million complex systems are randomly generated. Stability of each complex system is tested given variation in $\gamma$ by randomly sampling $\gamma \sim \mathcal{U}(0, 2)$. Stability given $Var(\gamma)$ is then compared to stability in an otherwise identical system in which $\gamma = E[\mathcal{U}(0, 2)]$ for all components. Red and black bars show the number of stable systems in the absence and presence of variance in $\gamma$, respectively. Blue lines show the proportion of systems that are stable when $Var(\gamma) > 0$, but would be unstable if $Var(\gamma) = 0$.

>>>>

**Figure 3: Stability of large complex systems with and without variation in component response rate ($\boldsymbol{\gamma}$).** The $\ln$ number of systems that are stable across different system sizes ($S$) given $C = 1$, and the proportion of systems in which variation in $\gamma$ is critical for system stability. For each $S$, 1 million complex systems are randomly generated. Stability of each complex system is tested given variation in $\gamma$ by randomly sampling $\gamma \sim \mathcal{U}(0, 2)$. Stability given $Var(\gamma)$ is then compared to stability in an otherwise identical system in which $\gamma = E[\mathcal{U}(0, 2)]$ for all components. Light and dark grey bars show the number of stable systems in the absence and presence of variance in $\gamma$, respectively. The black line shows the proportion of systems that are stable when $Var(\gamma) > 0$, but would be unstable if $Var(\gamma) = 0$.
